---
title: "Heat Hack 2022"
author: "Francesca Chiappetta"
date: "4/23/2022"
output: html_document
---


Variables 
Total Expenditure (USD)	Combined annual gas and electric expenditure per household in the census block group.	[29,37,60]
Building Size (ft2)	Average total floor area in square feet of each building within the census block group.	[6,11]
Median Building Age (years old)	Median building age in years, calculated by subtracting the year built from 2016.	[61]
Lot Size (acres)	Average total land area of the parcel upon which the building sits, measured in acres.	[27]
Building Density	Number of single-family residential buildings divided by the total area of the census block group.	[20,62,63]
Average Household Size	Average number of residents in a single housing unit in the census block group.	[6,11,17]
Median Household Income	Median household income of the census block group.	[34]
% Renter Population	Percentage of renters in occupied housing unit population.	[64]
% White	Percentage of total census block group population that is Caucasian.	[36,51]
% African American	Percentage of total census block group population that is African American.	[34,36]
% Hispanic/Latino	Percentage of total census block group population that is Hispanic or Latino.	[34]
% Bachelor's Degree or Higher	Percentage of total census block group population over the age of 25 that holds a Bachelor's degree or higher.	[34,61]
% 65 or Older	Percentage of total census block group population that is at least 65 years old.	[37,61]
% 18 or younger	Percentage of total census block group population that is 18 years or younger.	[37,61]
Average Morning Temperature	The average annualized morning temperature used to measure urban heat at the Census Block Group scale.	[37,65]
Average Afternoon Temperature	The average annualized afternoon temperature used to measure urban heat at the Census Block Group scale.	[37,65]
Average Evening Temperature	The average annualized evening temperature used to measure urban heat at the Census Block Group scale.	[37,65]


```{r libraries}
library(tidyverse)
library(tidycensus)
library(sf) #this is the spatial package
library(tmap) #this is the mapping
library(rmapshaper)
library(ggplot2)
library(spdep)
library(sf)
library(rgdal)
library(raster)
```

```{r read data, include=FALSE}

tract <- read.csv("/Users/frankiechiappetta/Desktop/DUKE/coding_workshops/downloaded_data/download/DurhamNeighborhoodCompass-tract.csv")

block <- read.csv("/Users/frankiechiappetta/Desktop/DUKE/coding_workshops/downloaded_data/download/DurhamNeighborhoodCompass-blockgroup.csv")


```

```{r read data}
shapefile <- st_read("/Users/frankiechiappetta/Desktop/DUKE/coding_workshops/downloaded_data/download/geography/blockgroups/durham_blockgroups.shp")


shapefile$id <- as.double(shapefile$id)
glimpse(shapefile)
```


```{r merge data}
merged <- merge(x = shapefile, y = block, by.x = "id", by.y = "Geography.Id")  
#glimpse(merged)
merged$geometry


```
```{r clean data}

#cleaning electicity data
merged$Avg..Monthly.Household.Electricity.Use..2013<-gsub("[^0-9.-]", "", merged$Avg..Monthly.Household.Electricity.Use..2013)

merged$Avg..Monthly.Household.Electricity.Use..2013 <- as.double(merged$Avg..Monthly.Household.Electricity.Use..2013)


merged$Avg..Monthly.Household.Electricity.Use..2014<-gsub("[^0-9.-]", "", merged$Avg..Monthly.Household.Electricity.Use..2014)

merged$Avg..Monthly.Household.Electricity.Use..2014 <- as.double(merged$Avg..Monthly.Household.Electricity.Use..2014)

```


```{r plotting}

#plotting monthly household electricity use in 2013
tm_shape(merged) + tm_polygons(col="Avg..Monthly.Household.Electricity.Use..2013", border.col = "white") + 
  tm_legend(outside = TRUE)

#plotting monthly household electricity use in 2014
tm_shape(merged) + tm_polygons(col="Avg..Monthly.Household.Electricity.Use..2014", border.col = "white") + 
  tm_legend(outside = TRUE) 

```
```{r read in more data}

#read in heat index data
readxl::read_xlsx("/Users/frankiechiappetta/Desktop/DUKE/coding_workshops/heat-hack-2022/Data/Aggregated by Block Groups/RD_Aggregated_BG_LC_Data_0331.xlsx", sheet = 2)

blocks_df <- st_read("/Users/frankiechiappetta/Desktop/DUKE/coding_workshops/heat-hack-2022/Data/Aggregated by Block Groups/Spatial_Data_BG/RD_BG_LC_0404.shx")

#heat index AM_HI 
#heat index AM_HI 
```

```{r map heat index}

#map Heat index data in the am, the afternoon, and the night
tm_shape(blocks_df) + tm_polygons(col="am_hi", border.col = "white") + 
  tm_legend(outside = TRUE) 
tm_shape(blocks_df) + tm_polygons(col="af_hi", border.col = "white") + 
  tm_legend(outside = TRUE) 
tm_shape(blocks_df) + tm_polygons(col="pm_hi", border.col = "white") + 
  tm_legend(outside = TRUE) 


```


```{r merge heat index and mega datasets}
blocks_df

#we have to make them dataframes
merged <- merged %>% as.data.frame()
blocks_df <-  blocks_df %>% as.data.frame()

names(blocks_df)[names(blocks_df) == 'GEOID10'] <- 'id'
blocks_df$id <- as.double(blocks_df$id)

df <- inner_join(merged, blocks_df, by = "id")

#and then make them geometry objects again
df %>% st_sf(sf_column_name = 'geometry.x')
```



```{r}

#LINEAR REGRESSION WOOOOSHOO
model <- lm(Avg..Monthly.Household.Electricity.Use..2014 ~ am_hi + af_hi + pm_hi + Asian.Population..2015, data = df)
summary(model)
```



